Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-01 analysis.tex
fixed some wording about delays
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@815 ccdd05d5-56c1-461a-bf98-85f6876523b4

The \fir\ filter banks are implemented using a \gstlal\ element called {\tt
lal\_firbank}, which produces N channels of filter output from an NxM matrix of
\fir\ filter coefficients.  This element is used in parallel branches in the
pipeline to implement the filtering of the SVD basis filters in each time
slice.  Rather than implement the time sliced templates as zero padded \fir\
filters as described in \eqref{FIXME} we instead implement them as shorter, but
appropriately time advanced \fir\ filters that contain only the nonzero
samples.  Adding the appropriate time offset to the filter output makes up for
the lack of explicit zero padding.  The orthogonal filter outputs must be
reconstructed into the filter output for the underlying physical filter ouputs.

>>>>

The \fir\ filter banks are implemented using a \gstlal\ element called {\tt
lal\_firbank}, which produces N channels of filter output from an NxM matrix of
\fir\ filter coefficients.  This element is used in parallel branches in the
pipeline to implement the filtering of the SVD basis filters in each time
slice.  Rather than implement the time sliced templates as zero padded \fir\
filters as described in \eqref{FIXME} we instead implement them as shorter
filters that contain only the nonzero samples.  Adding the appropriate time
offset to the filter output later in the pipeline makes up for the lack of
explicit zero padding.  The orthogonal filter outputs must be reconstructed
into the filter output for the underlying physical filter ouputs.
